### 2014-03-15 src/paper.Rnw
Fix column names to use correct letters

sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
new.colnames <- c('operator', 'r^2',      'm.red',            'm.sd',         'num',    'B*')
stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.

>>>>

sel.colnames <- c('operator', 'r.square', 'mutant.reduction', 'sd.reduction', 'sample', 'score.multiplier')
new.colnames <- c('operator', '$R^2$',      '$\\mu_{red}$',            '$\\sigma_{red}$',         'valid',    '$\\beta_1$')
stats.xp <- subset(stats.df, grepl('^(r|rr|rc)[.]', operator)) # We are ignoring ceil here. add rc if needed.
